---
title: "Data analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{data-download}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rGeoCBI)
library(ruODK)
library(magrittr)
library(leaflet)
library(reactable)
```

This vignette will provide a worked example of accessing and downloading the
burn grading submissions, and calculating the GeoCBI from the raw data.

Coming soon!

## Setup ruODK

Configure `.Renviron`. Restart session. `ru_setup(svc="")`.

## Download data

Use ruODK to download submissions from ODK Central.

## Calculate GeoCBI

Parse raw data into numeric scale values, apply GeoCBI formula.

## Visualise

```{r}
leaflet::leaflet(width = 800, height = 600) %>%
    leaflet::addProviderTiles("Esri.WorldImagery", group = "Aerial") %>%
    leaflet::addProviderTiles("OpenStreetMap.Mapnik", group = "Place names") %>%
    leaflet::clearBounds() %>%
    leaflet::setView(130,-33, 4) %>% 
    # add data here
      leaflet::addLayersControl(
        baseGroups = c("Aerial", "Place names"),
        # overlayGroups = "",
        options = leaflet::layersControlOptions(collapsed = FALSE)
      )

```

Here we'll show the actual data soon.

```{r}
data("mtcars")
head(mtcars) %>% reactable::reactable(sortable = T, filterable = T)
```
